\section{Introduction}
I propose to develop a general approach for incorporating prognostic
data into the control loop of autonomous systems.  The current
practice of prognostic control generally consists of using prognostic
data to inform human operators of impending failures, and then the
operator uses this information to inform operation and repair of the
system under observation.  By contrast, the current work seeks to use
prognostic data to augment the control strategy of a system during
operation, with the primary objective of extending the life of a
system without operator intervention.  This approach aims to be an
improvement over traditional fault tolerant control techniques in that
it will avert faults, instead of handling faults that have already
occured.

There are several difficulties in achieving this sort of
self-corrective system.  The first problem extends from the nature of
prognostic forecasting.  Because it is impossible to know the true
future state of a system, prognostic data always carries an element of
uncertainty.  The second problem is that a system will be undergoing
damage as it enters a state where the proposed corrective action will
be required, which means that an a priori control model will not
necessarily match the reality of the systems degraded operation.
Moreover, the proposed method would modify the behavior of the system
during a very dynamic period in its operation, making the control
model even more difficult to construct.  This pairing of uncertainty
under dynamic control is the main focus of my research.



\subsection{Definition of Terms}
\subsection{Anticipated Contributions}
\subsection{Organization of the Proposal}
