\chapter*{Vita} \label{ch:vita}
Robert Lowe was born in Knoxville Tennessee on June 9, 1980.  He had
his first programming experience at the age of 8 on his family's
Commodore Vic-20 computer.  Throughout middle and high school he
worked diligently to get as much computer time as he possibly could,
continuing his BASIC and assembler programming.
In high school he took up C and C++ programming, and was amazed to
discover that people could actually make a career out of computer
programming.

After graduating South Doyle High School in 1998, Robert attended
Middle Tennessee State University for three years, and then left to
work for Business Information Systems, a government contracting
company.  After working on several systems for government record
keeping, Robert returned to MTSU in 2005 and finished his BS in
Computer Science that same year.  Upon graduation, Robert Joined JC
Reed, a financial conglomerate, and also took a part-time teaching
position at Draughon's Junior College in Murfreesboro.  This latter
position blossomed into a life long love of teaching and academia.
after leaving JC Reed, Robert worked as an independent contractor for
several years before entering graduate school at the University of
Tennessee in 2008.

During graduate school, Robert supported his growing family by working
as an independent software developer and adjunct instructor at
Pellissippi State Community College, ITT Technical Institute,
Knoxville College, and Maryville College.  He also worked as a
teaching assistant and research assistant at UT.  These efforts
resulted in a full time tenure track position at Maryville College, a
position which Robert started in 2014.

Currently, Robert Lowe is the sole computer scientist on the full time
faculty of Maryville College.  Upon graduation, he plans to continue
teaching at Maryville College.
